---
---

## Introduction
This is one of the R functions produced to support the development of a package dedicated to the eLTER Research Infrastructure (eLTER RI). In this case it’s about how to generate QR Code of [**eLTER-RI sites or network**](https://deims.org/models) by [**DEIMS-ID**](https://deims.org/docs/deimsid.html) and using [**qrencoder package**](https://github.com/hrbrmstr/qrencoder).

## Data
Import `csv file` into R and verify the content.
```{r Import data}
suppressPackageStartupMessages(library(DT))
# Import Networks list
networksLTER <- utils::read.csv2("../nameCoordsNetworks.csv", header = T, sep = ",")
# Import Sites list
sitesLTER<- utils::read.csv2("../nameCoordsSites.csv", header = T, sep = ";")
```

### LTER Networks
```{r LTER Networks DataTable}
DT::datatable(networksLTER)
```

### LTER Sites
```{r LTER Sites DataTable}
DT::datatable(sitesLTER)
```

## QR Codes
### Prerequisite:
install qrencoder by
```{r}
devtools::install_github("hrbrmstr/qrencoder")
suppressPackageStartupMessages(library(qrencoder))
```

[**qrencoder package**](https://github.com/hrbrmstr/qrencoder) allows to create QRCode, without limit.
The QR Code generate below is about [**LTER-Italy Network**](https://deims.org/f30007c4-8a6e-4f11-ab87-569db54638fe). The URL of this network is collected by networks LTER dataframe imported above.

```{r QRCODE Network, warning=FALSE}
urlSite <- as.character(networksLTER$URL[12])
par(mar = c(0,0,0,0))
image(qrencode_raster(urlSite), 
      asp=1, col=c("white", "#000000"), axes=FALSE, 
      xlab="", ylab="")
```

The QR Code generate below is about [**Lago Maggiore LTER-Italy site**](https://deims.org/f30007c4-8a6e-4f11-ab87-569db54638fe). The URL of this network is collected by sites LTER dataframe imported above.
```{r QRCODE Site}
urlSite <- as.character(sitesLTER$deimsid[79])
par(mar = c(0,0,0,0))
image(qrencode_raster(urlSite), 
      asp=1, col=c("white", "#0578BE"), axes=FALSE, 
      xlab="", ylab="")
```

## Function eLTER_QRCode
```{r}
eLTER_QRCode <- function(deimsid) {
  par(mar = c(0,0,0,0))
  image(qrencode_raster(as.character(deimsid)), 
      asp=1, col=c("white", "#000000"), axes=FALSE, 
      xlab="", ylab="")
}

eLTER_QRCode('https://deims.org/f30007c4-8a6e-4f11-ab87-569db54638fe')
```

